\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2024-01-10 Articles/Article1-Conference/root.tex
added short summary of existing methods

Kinematic redundancy enables a kinematically redundant manipulator to follow a predefined task space trajectory using the endeffector (EE), while simultaneously, executing an additional task with the remaining movement capacity without impacting the trajectory adherence. This is possible because the robot's degrees of freedom (DOF) go beyond what is required to perform the primary task. Consequently, the robot can adopt different joint configurations optimised according to the secondary task while performing the primary task. Common secondary tasks include avoiding singularities, optimising the manipulability measure, minimising joint torques and avoiding obstacles in the operating space.

\add{reference za posamezne pristope, dela \\}

% PREDSTAVITEV PRISTOPOV PLANIRANJA POTI V ROBOTIKI
\add{Sampling based, Kinematic Optimizazion (LS, LQP), GCS, Learning-based, DMP(Hoffman), Trajectory Optimization.
\\}

Motion planning is a fundamental problem in robotics \cite{IDEASLab2023}. It consists of finding a sequence of joint configurations for a robot so that the robot can move along this path from its initial configuration to the goal configuration without colliding with static obstacles or other robots in the environment. In addition to collision avoidance, motion planning for manipulators can optionally take into account various constraints, such as position, velocity, acceleration or jerk constraints for the joint angle or end effector, precision of the end effector with respect to position and orientation, stability of the manipulator, avoidance of singularities, or any number of other criteria.

>>>>

Kinematic redundancy enables a manipulator to follow a predefined task space trajectory using the endeffector (EE), while simultaneously, optimising for an additional task with the remaining movement capacity without impacting the trajectory adherence. This is possible because the robot's degrees of freedom (DOF) go beyond what is required to perform the primary task. Consequently, the robot can adopt different joint configurations optimised according to the secondary task while performing the primary task. Common secondary tasks include avoiding singularities, optimising the manipulability measure, minimising joint torques and avoiding obstacles in the operating space.

\add{citations}

% PREDSTAVITEV PRISTOPOV PLANIRANJA POTI V ROBOTIKI

Motion planning~\cite{IDEASLab2023} is a fundamental problem in robotics. It consists of finding a sequence of joint configurations for a robot so that the robot can move along this path from its initial configuration to the goal configuration without colliding with static obstacles or other robots in the environment. In addition to collision avoidance, motion planning for manipulators can optionally take into account various constraints, such as position, velocity, acceleration or jerk constraints for the joint angle or end effector, precision of the end effector with respect to position and orientation, stability of the manipulator, avoidance of singularities, or any number of other criteria.

There are numerous methods for planning manipulator movements. Sampling-based methods such as PRM, RRT, RRT*, RRT-Connect, Informerd RRT*, BIT* and others offer a solution based on a global search in configuration space. However, the generated trajectories are not always smooth or optimal, and the performance of the methods may be insufficient for real-time operation. Recently, a number of learning-based methods using data-driven techniques have been proposed to improve or accelerate the functionality of sampling-based methods. \add{examples} Trajectory optimisation methods such as CHOMP, STOMP and TrajOpt, on the other hand, use optimization to improve an initial seed trajectory. Consequently, the optimality of the solution is highly dependent on this initial trajectory. Nevertheless, these methods are capable of generating smooth trajectories, and although they can be too computationally intensive for dynamic real-time environments, they are generally effective in finding constrained motion plans. The inverse kinematics with task prioritisation, which is based on finding a locally optimal least squares solution, and linear quadratic programming are two of the local optimization methods. Both methods are fast, suitable for real-time applications in dynamic environments and provide smooth solutions. However, since they do not plan further than one step ahead, they tend to get stuck in local minima. Therefore, they are often integrated with a higher-level planner, usually based on sampling, for global path search, while local optimisation takes dynamic environment changes into account.

\add{citations}
